---
title: "HW4"
author: "Korawat Tanwisuth"
date: "March 9, 2018"
output:
  pdf_document: default
  html_document: default
---
##1

maximize $0.05*(L^{2/3})*(K^{1/3})$<br/>

subject to $12*L+15*K \leq 100000$<br/>

```{r}
f <- function(x){
    return(-0.05*(x[1]^(2/3))*(x[2]^(1/3)))
}
gradf <- function(x){
    v1 <- (-0.05)*(2/3)*(x[1]^(-1/3))*(x[2]^(1/3))
    v2 <- (-0.05)*(1/3)*(x[2]^(-2/3))*(x[1]^(2/3))
    return(c(v1,v2))
}

ui <- matrix(c(-12,-15),ncol = 2)
ci <- matrix(c(-100000),ncol = 1)
ans1 <- constrOptim(c(5500,2200),f, grad=gradf, ui, ci)
-ans1$value
```


##2
Let $w_i = \text{the weight invested in stock i}\ i=1,2,\dots,n$<br/>
    $X_i = \text{return of stock i}\ i=1,2,\dots,n$<br/>
    $m_i = \text{mean return of stock i}\ i=1,2,\dots,n$<br/>
    
minimize $\sum_{i=1}^{n}w_i*w_j*Cov(X_i,X_j)\ \forall i,j$<br/>
subject to $\sum_{i=1}^{n}w_i=1\ \forall i$<br/>
           $\sum_{i=1}^{n}w_i*m_i\geq 0.01\ \forall i$<br/>
           $w_i \geq 0\ \forall i$<br/>
```{r}
library(quadprog)
stocks <- read.csv("homework4stocks.csv")
dates <- stocks[,1]
stock_ret <- stocks[,2:ncol(stocks)]
mean_ret <- apply(stock_ret,2,mean)
var_ret <- apply(stock_ret,2,var)
cor_ret <- cor(stock_ret)
n <- ncol(stock_ret)
A <- rbind(rep(1,n),mean_ret,diag(n))
Amat <- t(A)
Dmat <- 2*cov(stock_ret)
dvec <- rep(0,n)
bvec <- c(1,0.01,rep(0,n))
ans2 <- solve.QP(Dmat, dvec, Amat, bvec, meq=1)
sol <- ans2$solution
exp_mean <- sum(sol*mean_ret)
exp_var <- sum(sol*var_ret)
exp_sd <- sqrt(exp_var)
names(sol) <- colnames(stock_ret)
sol
```

```{r}
print(paste("Expected Mean", exp_mean))
print(paste("Expected Variance", exp_var))
print(paste("Expected Standard Deviation",exp_sd))
```



##3
```{r}
library(knitr)
df<- read.csv("variable_selection.csv")
lm2_1 <- lm(y~x1+x2,df)
lm2_2 <- lm(y~x1+x3,df)
lm2_3 <- lm(y~x2+x3,df)
lm1_1 <- lm(y~x1,df)
lm1_2 <- lm(y~x2,df)
lm1_3 <- lm(y~x3,df)
sse <- function(lm_ob){
    return(sum(lm_ob$residuals^2))
}
sse_vec <- c(sse(lm2_1),sse(lm2_2),sse(lm2_3),sse(lm1_1),sse(lm1_2),sse(lm1_3))
sse_names <- c("x1_x2","x1_x3","x2_x3","x1","x2","x3")
table_sse <- data.frame(sse_vec)
rownames(table_sse) <- sse_names
table_sse
```

This shows that the model with only $x_1$ and $x_2$ minimizes residual sum squared.

##4

Let $x_{ij} = \text{allowable path from node i to node j}\ \forall i,j$<br/>

minimize $I^2R$<br/>

subject to $x_{12}+x_{13}=710$<br/>
            $x_{12}-x_{23}-x_{24}=0$<br/>
            $x_{13}+x_{23}-x_{34}=0$<br/>
            $x_{24}+x_{34}=710$<br/>

```{r}
n <- 5
c1<- c(1,1,rep(0,3))
c2 <- c(1,0,-1,-1,0)
c3 <- c(0,1,1,0,-1)
c4 <- c(rep(0,3),1,1)
A <- rbind(c1,c2,c3,c4)
Amat <- t(A)
bvec <- c(710,0,0,710)
dvec <- rep(0,n)
Dmat <- matrix(0,n,n)
diag(Dmat) <- 2*c(1,4,6,12,3)
ans4<- solve.QP(Dmat, dvec, Amat, bvec, meq=length(bvec))$solution

```

```{r}
names(ans4) <- c("x_12","x_13","x_23","x_24","x_34")
ans4
```


##5

Let  $y_i = \text{actual spread of team i}$<br/>

$\hat{y} =\text{the predicted spread}\ \forall i=1,2,\dots,n$<br/>
    
minimize $\sum_{i=1}^{n}(y_i-\hat{y_i})^2$


```{r}
nfl <- read.csv("nflratings.csv",header = FALSE)
colnames(nfl) <- c("Week","HT_index","VT_index","HT_score","VT_score")
avg_rate <- 85
APS <- nfl["HT_score"]-nfl["VT_score"]
HT_index <- as.vector(nfl[["HT_index"]])
VT_index <- as.vector(nfl[["VT_index"]])

pred_spread <- function(HTR,VTR,HTA){
    return(HTR-VTR+HTA)
}
n <- max(HT_index)
pred_err <- function(x){
    x <- (x-mean(x))+avg_rate
    HTR <- x[HT_index]
    VTR <- x[VT_index]
    HTA <- x[length(x)]
    prediction <- pred_spread(HTR,VTR,HTA)
    return(sum((APS-prediction)^2))
}

guess <- rep(85,n+1)
res <-optim(guess,pred_err,method = "CG")
best_sol <- res$par
lowest <- res$val

lowest
best_sol
```

